A Gentle Introduction and Application of Feature-Based Clustering with Psychological Time Series

### 2023-08-11 Supplemental Material A - Illustration/Supplemental-Material-A-Illustration.tex
references updated

% formatting links in the PDF file
\hypersetup{
pdfpagemode={UseOutlines},
bookmarksopen=true,
bookmarksopenlevel=0,
hypertexnames=false,
colorlinks   = true, %Colours links instead of ugly boxes
urlcolor     = blue, %Colour for external hyperlinks
linkcolor    = blue, %Colour of internal links
citecolor   = black, %Colour of citations
pdfstartview={FitV},
unicode,
breaklinks=true,
}

@@

This supplementary information documents our tutorial-style illustration website. As part of our open supplemental materials, we share the full illustration as an interactive tutorial-style website. This file offers transparent and reproducible analysis code, which includes full author commentary. We rendered the Quarto project as an interactive HTML website, which we host as part of our open GitHub repository. We recommend the rendered version for almost all readers (full R code is also available via the rendered version).

\vspace{.5cm}
\begin{tcolorbox}
    \vspace{0.2cm} \centering 
    \href{https://janniscodes.github.io/ts-feature-clustering-illustration/}{https://janniscodes.github.io/ts-feature-clustering-illustration/}
    \vspace{0.2cm} 
\end{tcolorbox}

For readers interested in the raw files, the raw Quarto files are available in our OSF repository \citep[see][]{KreienkampMasked-clust-osf} and can also be accessed as part of the full GitHub repository \citep[][]{KreienkampMasked-clust-github}.

>>>>

% formatting links in the PDF file
\definecolor{googleurlcolor}{HTML}{1a0dab}
\hypersetup{
pdfpagemode={UseOutlines},
bookmarksopen=true,
bookmarksopenlevel=0,
hypertexnames=false,
colorlinks   = true, %Colours links instead of ugly boxes
urlcolor     = googleurlcolor, %blue,Colour for external hyperlinks
linkcolor    = black, %blue, Colour of internal links
citecolor   = black, % cyan, Colour of citations
pdfstartview={FitV},
unicode,
breaklinks=true,
}

@@

This supplementary information documents our tutorial-style illustration website. As part of our open supplemental materials, we share the full illustration as an interactive tutorial-style website. This file offers transparent and reproducible analysis code, which includes full author commentary. We rendered the Quarto project as an interactive HTML website, which we host as part of our open GitHub repository \citep{KreienkampMasked-illustration-github}. We recommend the rendered version for almost all readers (full R code is also available via the rendered version).

\vspace{.5cm}
\begin{tcolorbox}
    \vspace{0.2cm} \centering 
    \href{https://janniscodes.github.io/ts-feature-clustering-illustration/}{www.tsFeatureClustR.com}
    \vspace{0.2cm} 
\end{tcolorbox}

For readers interested in the raw files, the raw Quarto files are available in our OSF repository \citep[see][]{KreienkampMasked-clust-osf} and can also be accessed as part of the project GitHub repository \citep[][]{KreienkampMasked-clust-github}.

### 2023-08-11 TitlePage.tex
references updated

% formatting links in the PDF file
\hypersetup{
pdfpagemode={UseOutlines},
bookmarksopen=true,
bookmarksopenlevel=0,
hypertexnames=false,
colorlinks   = true, %Colours links instead of ugly boxes
urlcolor     = blue, %Colour for external hyperlinks
linkcolor    = blue, %Colour of internal links
citecolor   = cyan, %Colour of citations
pdfstartview={FitV},
unicode,
breaklinks=true,
}

@@

% add reference library file
\addbibresource{references.bib}

% add reference library file
\addbibresource{references.bib}

% Title and header
\title{Migration Experience Trajectories: Subtitle TBD}
\shorttitle{Migration Experience Trajectories}

% Authors
\author[*,1,3]{Jannis Kreienkamp}
\author[1,3]{Laura F. Bringmann}
\author[1,3]{Kai Epstude}
\author[1,3]{Maximilian Agostini}
\author[1,3]{Peter de Jonge}
\author[2,3]{Rei Tendeiro-Monden}
\affiliation{\hfill}

\affil[1]{University of Groningen, Department of Psychology}
\affil[2]{Hiroshima University, Graduate School of Advanced Science and Engineering}
\affil[3]{Author order TBD [currently in first name alphabetical order]}

\authornote{
   \addORCIDlink{* Jannis Kreienkamp}{0000-0002-1831-5604}\\
   \addORCIDlink{Laura F. Bringmann}{0000-0002-8091-9935}\\
   \addORCIDlink{Maximilian Agostini}{0000-0001-6435-7621}\\
   \addORCIDlink{Kai Epstude}{0000-0001-9817-3847}\\
   \addORCIDlink{Peter de Jonge}{0000-0002-0866-6929}\\
   \addORCIDlink{Rei Monden}{0000-0003-1744-5447}

We have no known conflict of interest to declare. The authors received no specific funding for this work. Materials and  software is available at \url{https://janniscodes.github.io/migration-trajectories/}  \citep{KreienkampTBD}. Protocols, materials, data, and code are available at \url{https://osf.io/TBA} \citep{KreienkampTBD}. The preregistration of our analysis can be accessed as part of our Open Science Framework repository \citep{KreienkampTBD}.

Correspondence concerning this article should be addressed to Jannis Kreienkamp, Department of Psychology, University of Groningen, Grote Kruisstraat 2/1, 9712 TS Groningen (The Netherlands).  E-mail: j.kreienkamp@rug.nl}

@@

% add title information (incl. title page and abstract)
\maketitle

>>>>

% formatting links in the PDF file
\definecolor{googleurlcolor}{HTML}{1a0dab}
\hypersetup{
    pdfpagemode={UseOutlines},
    bookmarksopen=true,
    bookmarksopenlevel=0,
    hypertexnames=false,
    colorlinks   = true, %Colours links instead of ugly boxes
    urlcolor     = googleurlcolor, %blue,Colour for external hyperlinks
    linkcolor    = black, %blue, Colour of internal links
    citecolor   = black, % cyan, Colour of citations
    pdfstartview={FitV},
    unicode,
    breaklinks=true,
}

@@

% custom open science badge height
\newlength{\badgeheight}
\setlength{\badgeheight}{1em}

% add reference library file
\addbibresource{referencesZotero.bib}

% Title and header
\title{A Gentle Introduction and Application of Feature-Based Clustering with Psychological Time Series\\}
\shorttitle{feature-based time series clustering}

% Authors
\author[*,1]{Jannis Kreienkamp}
\author[1]{Maximilian Agostini}
\author[2]{Rei Monden}
\author[1]{Kai Epstude}
\author[1,3]{Peter de Jonge}
\author[1,3]{Laura F. Bringmann}
\affiliation{\hfill}

\affil[1]{University of Groningen, Department of Psychology}
\affil[2]{Hiroshima University, Graduate School of Advanced Science and Engineering}
\affil[3]{Interdisciplinary Center Psychopathology and Emotion Regulation}

\authornote{   
   \addORCIDlink{* Jannis Kreienkamp}{0000-0002-1831-5604}\\
   \addORCIDlink{Maximilian Agostini}{0000-0001-6435-7621}\\
   \addORCIDlink{Rei Monden}{0000-0003-1744-5447}\\
   \addORCIDlink{Kai Epstude}{0000-0001-9817-3847}\\
   \addORCIDlink{Peter de Jonge}{0000-0002-0866-6929}\\
   \addORCIDlink{Laura F. Bringmann}{0000-0002-8091-9935}

We have no known conflict of interest to declare. The authors received no specific funding for this work. Materials, data, and code are available at \url{https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4} \citep{Kreienkamp-clust-osf}. Materials and software are also available as part of our project GitHub repository \citep{Kreienkamp-clust-github}. The full illustration code is also available as a tutorial-style website at \href{https://tsfeatureclustr.com}{www.tsFeatureClustR.com} \citep{Kreienkamp-illustration-github}.

Correspondence concerning this article should be addressed to Jannis Kreienkamp, Department of Psychology, University of Groningen, Grote Kruisstraat 2/1, 9712 TS Groningen (The Netherlands).  E-mail: \href{mailto:j.kreienkamp@rug.nl}{j.kreienkamp@rug.nl}

\vspace{1em}
\textit{Open Science Practices:}
    \href{https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4}{\includegraphics[height=\badgeheight]{assets/open-badges-small/material-color.png}} Open Materials, 
    \href{https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4}{\includegraphics[height=\badgeheight]{assets/open-badges-small/data-color.png}} Open Data,
    \href{https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4}{\includegraphics[height=\badgeheight]{assets/open-badges-small/code-color.png}} Open Code, \break
    \href{https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4}{\includegraphics[height=\badgeheight]{assets/open-badges-small/supplements-color.png}} Open Supplements

}

@@

% add title information (incl. title page and abstract)
%\maketitle

\makeatletter
\vspace*{2em}
\begin{center}
\noindent \textbf\@title
\vspace{1em}
\noindent \@author
\end{center}
\vspace{2em}
\begin{center}%
    \textbf\acksname%
\end{center}%
\vspace{-1em}
\protect\raggedright
\setlength{\parindent}{0.5in}
\indent\par\@acks%

### 2023-08-11 manuscript.tex
references updated

\keywords{
    time series analysis, feature-based clustering, intensive longitudinal data, ESM\\
    \vspace{1em}
    \textit{Open Science Practices:}
    \href{https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4}{\includegraphics[height=\badgeheight]{assets/open-badges-small/material-color.png}} Open Materials, 
    \href{https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4}{\includegraphics[height=\badgeheight]{assets/open-badges-small/data-color.png}} Open Data,
    \href{https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4}{\includegraphics[height=\badgeheight]{assets/open-badges-small/code-color.png}} Open Code, \break
    \href{https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4}{\includegraphics[height=\badgeheight]{assets/open-badges-small/supplements-color.png}} Open Supplements\\
    \vspace{1em}
    Materials and software are available as part of our project GitHub repository \citep{KreienkampMasked-clust-github}. The full illustration code is also available as a tutorial-style website \citep{KreienkampMasked-illustration-github}. Materials, data, and code are available at \url{https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4} \citep{KreienkampMasked-clust-osf}.
}

>>>>

\keywords{
    time series analysis, feature-based clustering, intensive longitudinal data, ESM\\
    \vspace{1em}
    \textit{Open Science Practices:}
    \href{https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4}{\includegraphics[height=\badgeheight]{assets/open-badges-small/material-color.png}} Open Materials, 
    \href{https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4}{\includegraphics[height=\badgeheight]{assets/open-badges-small/data-color.png}} Open Data,
    \href{https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4}{\includegraphics[height=\badgeheight]{assets/open-badges-small/code-color.png}} Open Code, \break
    \href{https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4}{\includegraphics[height=\badgeheight]{assets/open-badges-small/supplements-color.png}} Open Supplements\\
    \vspace{1em}
    Materials, data, and code are available at \url{https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4} \citep{KreienkampMasked-clust-osf}. Materials and software are also available as part of our project GitHub repository \citep{KreienkampMasked-clust-github}. The full illustration code is also available as a tutorial-style website at \href{https://tsfeatureclustr.com}{www.tsFeatureClustR.com} \citep{KreienkampMasked-illustration-github}.
}
